intro

### 2022-03-16 06_Paper/ER-ED/TheoreticalBackground.Rmd
test
test

Moreover, it is known that ER strategies <!-- all these strategies?--> reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG)[@Zaehringer2020] .
<!-- hier ist noch der Bezug zum Arousal drin gewesen, habe ich angepasst. Corrugator habe ich raus genommen, weil auch Levator untersucht wird (müssten sonst m.E. beide genannt werden.) Generell fehlt noch etwas die Einbettung, warum die beiden ausgewählt wurden. Soll ich da noch etwas ergänzen? bei Zaehringer wird der Levator überhaupt nicht genannt, die Metaanalyse bezieht sich nur auf den Corrugator. Wir hatten damals gesagt, dass viele der negativen Bilder primär auch recht eklig sind und daher der Levator passender sein könnte, weil er speuzifisch auf Ekel zu reagieren scheint, der Corrugator hingegen auf negative Bilder im Allgemeinen. Prinzipiell haben wir aber für beide die gleichen Hypothesen. Können aber auch warten, was die Reviewer sagen.--> 
<!-- Denise: Ja das ist noch ein schwächerer Punkt in der Intro. Ich habe auch nur Paper gefunden, die EMG corrugator und levator für negative valence berichten, levator eher für Ekel, aber das muss hier kommen. Ein Satz für EMG reicht nicht aus. Wenn ihr weder auf Valence noch auf Arousal (so wie ich bei den Hypothesen noch vorgeschlagen hatte) hier gehen möchtet, dann könnte man das Konstrukt ja muscle activation o.ä. nennen und dies dann im Methodenteil über EMG corrugator und levator operationalisieren. Ich denke aber, dass die getrennte Analyse der beiden Muskelgruppen nivht gerechtfertig ist, da ihr ja keine getrennten Effekte annehmt, sondern der levator eventuel noch sinnvoll ist, da wir viele Ekelbilder haben. Habt ihr schonmal überlegt einen index über beide Aktivierungen zu bilden und dann darüber die Muskelaktivierung zu operationalisieren? Würde die Hypothesen und auch die Interpretation einfacher machen. Falls das nichts bringt, kann man explorativ immer noch die beiden EMGs getrennt analysieren und dies dann so berichten. -->
Similarly to the differences in short term effectiveness, these tactics from three different strategies are also related to different medium and long-term consequences. 
In particular, strategies that do not change the emotional content of the situation, for instance by taking a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being [@GrossJohn2003]. 
In addition, a number of ER strategies have been associated with mental disorders (for meta-analytic review, see Aldao et al. [@Aldao2010]), which led to the postulation of *adaptive* and *maladaptive* ER strategies.
For example, it was shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].

@@

How do people choose strategies from their repertoire? 
Similarly to the expectancy-value model of emotion regulation [@Tamir2015] it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
Evidence from other psychological domains (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made. 
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs[@Sheppes2014]. 
For example, a study found that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction [@Sheppes2011;@Sheppes2014].
ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy [@Scheffel2021].
In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
This could be seen as an indirect evidence that subjective effort has an influence on SVs of ER strategies
 <!-- Denise: Ist das so? Na gut, es gibt schon einiges an Choice und Goals, aber zu Effort als reason? Ich bin nicht ganz überzeugt davon, dass die Argumentation sich ab hier vor allem auf die nicht gewählte Strategie fokussiert. Kann man nicht auch sagen, dass es noch zu wenig zu effort gibt, das Scheffel2021 eine der ersten war, die mehrere Strategien hinsichtlich effort mit subjektiven, physiologischen und Verhaltensmaßen untersucht hat, dass sich nun die Frage stellt, was genau der subjektive Effort macht, nämlich den Subjective Value beeinflussen, dass dies eben auch für die gewählte Strategie oder im Vergleich mehrerer Taktiken noch nicht untersucht wurde. Und das ihr deshalb nun so vorgeht? -->

We assume that people choose the strategy that has the highest value for them at the moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement [@Aldao2015]. 
One certainly central goal is the regulation of negative affect.
A second, intrinsic and less obvious goal is the avoidance of effort [@Inzlicht2018].
When given the choice, most individuals prefer tasks that are less effortful [@Hull1943].
We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
SVs of ER Strategies could therefore be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibility, however, would show high SVs only for one or very few strategies.
This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from. 
Subsequently, the ability to choose an appropriate strategy for a specific situation is also limited.

@@

The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
As a manipulation check, we first want to investigate whether the valence (neutral, negative) of the pictures is effecting subjective and physiological responding (EMG).
Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological responding as well as, third, whether they require cognitive effort. 
The following hypotheses are proposed:
<!-- es gibt bisher noch keine Begründnung/Einbettung der nachfolgenden Hypothesen. Z.B.: Warum wird Corrugator und Levator untersucht? m.E. müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.--> <!-- Denise: ja, das hab ich auch bemerkt, ist EMG auch arousal? Dann dies erstens noch einführen und argumentieren und dann auch als physiological arousal aufführen. oder steht corrugator für arousal und levator für valence? dann auch so benennen. Außerdem subjective arousal/ subjective effort auch immer konsistent benennen. Ich schlage vor hier in den hypothesen immer von subjective arousal / effort zu sprechen, dies dann im Methodenteil über die subjective ratings / effort ratings zu operationalisieren (fehlt übrigens im Methodenteil noch.-->
<!-- Denise: im analysis plan habt ihr auch den vergleich negative vs. neutral (active viewing) beschrieben, deshalb hab ich das hier mal als Hypothese aufgenommen-->

* H1a) Subjective arousal is lower after actively viewing neutral pictures compared to actively viewing negative pictures. 
* H1b) Physiological responding (EMG *corrugator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
* H1c) Physiological responding (EMG *levator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.

* H2a) Subjective arousal (arousal rating) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H3a) Physiological responding (EMG *corrugator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H3b) Physiological responding (EMG *levator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.

* H4a) Subjective effort (effort rating) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H3b) The majority of participants re-uses the strategy that was least effortful for them.

>>>>

Psychophysiology provides further important information on the effectiveness of emotion regulation strategies.
Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromoygraphy has been reported consistently across studies to be influenced by emotion regluation with even medium effect sizes [@Zaehringer2020].
For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the Corrugtor muscle (associated with anger, sadness, and fear) and the levator muscle (associated with disgust) with _d~-~_ = 0.32 ([@Zaehringer2020]) and _d~-~_ = XXX (XXX), respectively. 
Similar effects have been reported for suppression (XXX) and distancing/distraction (XXX).

einführen als Valenz: hier und/oder weiter unten!!!
test von heute

<!-- hier ist noch der Bezug zum Arousal drin gewesen, habe ich angepasst. Corrugator habe ich raus genommen, weil auch Levator untersucht wird (müssten sonst m.E. beide genannt werden.) Generell fehlt noch etwas die Einbettung, warum die beiden ausgewählt wurden. Soll ich da noch etwas ergänzen? bei Zaehringer wird der Levator überhaupt nicht genannt, die Metaanalyse bezieht sich nur auf den Corrugator. Wir hatten damals gesagt, dass viele der negativen Bilder primär auch recht eklig sind und daher der Levator passender sein könnte, weil er speuzifisch auf Ekel zu reagieren scheint, der Corrugator hingegen auf negative Bilder im Allgemeinen. Prinzipiell haben wir aber für beide die gleichen Hypothesen. Können aber auch warten, was die Reviewer sagen.--> 
<!-- Denise: Ja das ist noch ein schwächerer Punkt in der Intro. Ich habe auch nur Paper gefunden, die EMG corrugator und levator für negative valence berichten, levator eher für Ekel, aber das muss hier kommen. Ein Satz für EMG reicht nicht aus. Wenn ihr weder auf Valence noch auf Arousal (so wie ich bei den Hypothesen noch vorgeschlagen hatte) hier gehen möchtet, dann könnte man das Konstrukt ja muscle activation o.ä. nennen und dies dann im Methodenteil über EMG corrugator und levator operationalisieren. Ich denke aber, dass die getrennte Analyse der beiden Muskelgruppen nivht gerechtfertig ist, da ihr ja keine getrennten Effekte annehmt, sondern der levator eventuel noch sinnvoll ist, da wir viele Ekelbilder haben. Habt ihr schonmal überlegt einen index über beide Aktivierungen zu bilden und dann darüber die Muskelaktivierung zu operationalisieren? Würde die Hypothesen und auch die Interpretation einfacher machen. Falls das nichts bringt, kann man explorativ immer noch die beiden EMGs getrennt analysieren und dies dann so berichten. -->
<!-- Anne: EMG wird ganz eindeutig in der Literatur für Valenz verwendet (und EDA oder pupil dilation für Arousal), ich finde, das sollten wir hier auch so labeln. Falls das aus irgendeinenm Grund blöd erscheint, würde ich alternativ überall von physiological responses sprechen. Aber "physiological valence" passt m.E. am besten.-->

Similarly to the differences in short term effectiveness, these tactics from three different strategies are also related to different medium and long-term consequences. 
In particular, strategies that do not change the emotional content of the situation, for instance by taking a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being [@GrossJohn2003]. 
In addition, a number of ER strategies <!-- Anne: welche? siehe auch nöchster Kommentar, an irgendeiner Stelle würde ich ein zwei Beispiele nennen.--> have been associated with mental disorders (for meta-analytic review, see Aldao et al. [@Aldao2010]), which led to the postulation of *adaptive* (such as reappraisal, acceptance) and *maladaptive* (such as suppression, rumination) ER strategies.
For example, it was shown that maladaptive ER strategies <!-- Anne: hier würde ich die konkrete Strategie(n) in Klammer nennen--> mediate the effect between neuroticism and depressive symptoms [@Yoon2013].

@@

How do people choose strategies from their repertoire? 
Similarly to the expectancy-value model of emotion regulation [@Tamir2015] it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
Evidence from other psychological domains (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made. 
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs. 
For example, a study found that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction [@Sheppes2011;@Sheppes2014].
ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy [@Scheffel2021].
In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.<!-- Denise: und fehlen nicht auch noch mehr Studien, die speziell effort im Blick haben? -->
People choose a strategy that they prefer for different, relatively well-known reasons[@Sheppes2014]. <!-- Denise: Ist das so? Na gut, es gibt schon einiges an Choice und Goals, aber zu Effort als reason? Ich bin nicht ganz überzeugt davon, dass die Argumentation sich ab hier vor allem auf die nicht gewählte Strategie fokussiert. Kann man nicht auch sagen, dass es noch zu wenig zu effort gibt, das Scheffel2021 eine der ersten war, die mehrere Strategien hinsichtlich effort mit subjektiven, physiologischen und Verhaltensmaßen untersucht hat, dass sich nun die Frage stellt, was genau der subjektive Effort macht, nämlich den Subjective Value beeinflussen, dass dies eben auch für die gewählte Strategie oder im Vergleich mehrerer Taktiken noch nicht untersucht wurde. Und das ihr deshalb nun so vorgeht? -->

We assume that people choose the strategy that has the highest value for them at the moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement [@Aldao2015]. 
One certainly central goal is the regulation of negative affect.
A second, intrinsic and less obvious goal is the avoidance of effort [@Inzlicht2018].
When given the choice, most individuals prefer tasks that are less effortful [@Hull1943].
We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful. <!-- Genau, die Argumentation ist super, nur braucht ihr dafür oben den Hinweis auf die nicht gewählte Strategie?-->
SVs of ER Strategies could therefore be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibility, however, would show high SVs only for one or very few strategies.
This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from. 
Subsequently, the ability to choose an appropriate strategy for a specific situation is also limited.

@@

The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
As a manipulation check, we first want to investigate whether the valence (neutral, negative) of the pictures is effecting subjective and physiological responding (EMG).
Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological responding as well as, third, whether they require cognitive effort. 
The following hypotheses are proposed:
<!-- es gibt bisher noch keine Begründnung/Einbettung der nachfolgenden Hypothesen. Z.B.: Warum wird Corrugator und Levator untersucht? m.E. müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.--> <!-- Denise: ja, das hab ich auch bemerkt, ist EMG auch arousal? Dann dies erstens noch einführen und argumentieren und dann auch als physiological arousal aufführen. oder steht corrugator für arousal und levator für valence? dann auch so benennen. Außerdem subjective arousal/ subjective effort auch immer konsistent benennen. Ich schlage vor hier in den hypothesen immer von subjective arousal / effort zu sprechen, dies dann im Methodenteil über die subjective ratings / effort ratings zu operationalisieren (fehlt übrigens im Methodenteil noch.-->
<!-- Denise: im analysis plan habt ihr auch den vergleich negative vs. neutral (active viewing) beschrieben, deshalb hab ich das hier mal als Hypothese aufgenommen-->
<!-- Anne: Ich habe jetzt Corrugator und Levator mal zusammengefasst-->

* H1a) Subjective arousal is lower after actively viewing neutral pictures compared to actively viewing negative pictures. 
* H1b) Physiological responding (EMG *corrugator* and *levator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.

* H2a) Subjective arousal is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H2b) Physiological responding (EMG *corrugator* and *levator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.

* H3a) Subjective effort is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H3b) The majority of participants re-uses the strategy that was least effortful for them. <!-- Könnt ihr diese Hypothese statistisch testen? Finde im 'Analysis Plan' nicht, wie ihr das testen möchtet, das muss dort noch erklärt werden. Mein Vorschlag für diese Hypothese: When having free choice, participants re-use the strategy with less subjective effort.-->
